---
title: "Example workflow - DFO Maritimes MPAs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example workflow - DFO Maritimes MPAs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "ragg_png"
)
```

```{r setup}
library(marxanr)
library(ggplot2)
library(dplyr)
library(sf)
```

This vignette provides step by step guidance to take spatial data layers, transform these into Marxan inputs, run Marxan, then load and interpret the results.

# Loading data layers



## Spatial data
```{r}
data(pu)

# landmasses for plotting
data(land)

# x and y limits to make nicer plots
xlim <- st_bbox(pu)[c(1,3)]
ylim <- st_bbox(pu)[c(2,4)]
ggcoords <- coord_sf(xlim=xlim,
           ylim=ylim)

basemap <- ggplot(land)+
  geom_sf()

basemap+
  geom_sf(data=pu)+
  ggcoords
  
```

## Marxan data

Data for this example, which are included in this package, are derived from [Serdynska et al. 2021](https://open.canada.ca/data/en/dataset/2d9cce9a-d634-4b49-879f-87c40c52acf2) will be used in this example. These data are the available bioregional-scale ecological and human use data used to inform draft Marine Protected Area (MPA) design for the Scotian Shelf-Bay of Fundy Bioregion. Please see the [original technical report](https://publications.gc.ca/collections/collection_2021/mpo-dfo/Fs97-6-3382-eng.pdf) for further details.

*While the input data are "real", the following example is NOT to be interpreted in any way as a suggestion for real MPA placement. The example is to show that you CAN run Marxan via R with real data. The example has not been properly paramaterized or optimized.*

```{r}
data("spec")
data("puvspr")
data("pu_dat")
data("bound")

head(spec)
head(puvspr)
head(pu_dat)
head(bound)
```

# Creating a Marxan project folder
```{r}
# name for new scenario
scen <- "MPAtest"

```
```{r, eval=FALSE}
# create a folder for a new scenario
createMarxanFolder(scen=scen,dialog = FALSE)

# download marxan if necessary
downloadMarxan(path = scen)

# write marxan files to folder
write.csv(spec,file.path(scen,"input","spec.dat"),quote = FALSE,row.names = FALSE)
write.csv(puvspr,file.path(scen,"input","puvspr.dat"),quote = FALSE,row.names = FALSE)
write.csv(pu_dat,file.path(scen,"input","pu.dat"),quote = FALSE,row.names = FALSE)
write.csv(bound,file.path(scen,"input","bound.dat"),quote = FALSE,row.names = FALSE)

# create new input parameters
input <- newParams(BLM=10^5,NUMREPS = 50L,SCENNAME = scen)
writeParams(inputdat = input,file = file.path(scen,"input.dat"))

# run marxan
runMarxan(marxanpath = scen,
          inputdatfile = "input.dat")
# unlink(scen,recursive = TRUE) # if necessary
```

# Plotting results

```{r}
ssoln <- read.csv(file.path(scen,"output",paste0(scen,"_ssoln.csv"))) %>%
  mutate(planning_unit = as.character(planning_unit)) %>%
  right_join(pu,by=c("planning_unit"="id")) %>% 
  st_as_sf()
basemap+
  geom_sf(data = ssoln, aes(fill=number))+
  ggcoords

best <- read.csv(file.path(scen,"output",paste0(scen,"_best.csv"))) %>%
  mutate(PUID = as.character(PUID)) %>%
  right_join(pu,by=c("PUID"="id")) %>% 
  st_as_sf()
basemap+
  geom_sf(data = best, aes(fill=SOLUTION))+
  ggcoords

```

