---
title: "Example workflow - DFO Maritimes MPAs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example workflow - DFO Maritimes MPAs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(marxanr)
# library(sf)
# library(purrr)
```

This vignette provides step by step guidance to take spatial data layers, transform these into Marxan inputs, run Marxan, then load and interpret the results.

# Getting data layers

Data from [Serdynska et al. 2021](https://open.canada.ca/data/en/dataset/2d9cce9a-d634-4b49-879f-87c40c52acf2) will be used in this example. These data are the available bioregional-scale ecological and human use data used to inform draft Marine Protected Area (MPA) design for the Scotian Shelf-Bay of Fundy Bioregion. Please see the [original technical report](https://publications.gc.ca/collections/collection_2021/mpo-dfo/Fs97-6-3382-eng.pdf) for further details.

This first step is to download the raw data (if necessary).

```{r,eval=FALSE}
# if(!file.exists("../data-raw/MPA_NetworkDesign.gdb.zip")){
#   # download the archive
#   download.file("https://pacgis01.dfo-mpo.gc.ca/FGPPublic/Offshore_Ecological_Human_Use_MPA_Scotian%20Shelf/Download/MPA_NetworkDesign.gdb.zip","../data-raw/MPA_NetworkDesign.gdb.zip",timeout=300)
# 
#   # unzip
#   unzip("../data-raw/MPA_NetworkDesign.gdb.zip")
# 
#   # load select layers
#   layers <- sf::st_layers("../data-raw/MPA_NetworkDesign.gdb")
#   gdb <- purrr::map(layers$name[c(6,30,58)],function(l) st_read("../data-raw/MPA_NetworkDesign.gdb",l)) %>%
#     dplyr::bind_rows()
# 
# 
#   BiophysicalUnits <- st_read("MPA_NetworkDesign.gdb","BiophysicalUnits")
#   }
```

